\section{Background}

Android app security is reflected in several layers of evidence: manifest declarations, requested permissions, exported components, packaged resources, embedded libraries, native code, storage configuration, and network-security settings. Android permissions protect restricted data such as contacts and device state, as well as restricted actions such as recording audio or interacting with paired devices \cite{androidPermissions2026}. Android guidance also emphasizes minimizing permission requests, using privacy-preserving alternatives, protecting inter-application communication, and limiting unnecessary data access \cite{androidPrivacyChecklist2026,androidSecurityBestPractices2026}. These platform rules make the packaged application a useful starting point for analysis, but they do not make packaged evidence self-sufficient.

Static analysis provides a repeatable way to inspect packaged evidence before execution. ManiScope examined Android manifest correctness at ecosystem scale and identified missing, misplaced, and unexpected elements or attributes across Google Play and pre-installed applications \cite{yang2022maniscope}. Wang et al.\ studied runtime-permission failures and showed that application behavior can break or become unsafe when developers do not correctly handle permission revocation, asynchronous execution, and differences across Android versions \cite{wang2023runtimepermissions}. These findings support static inspection as a method for identifying structural exposure, while also showing that permissions and manifest declarations alone cannot establish runtime behavior or privacy impact.

Dynamic analysis complements static evidence by observing an application under controlled runtime conditions. A recent systematic review identifies execution coverage, environmental dependence, nondeterminism, stimulation strategy, and experiment provenance as continuing challenges in Android dynamic analysis \cite{sutter2024dynamic}. Physical-device acquisition can provide realistic runtime evidence without requiring a rooted or heavily modified environment. Neth et al.\ demonstrated that ADB-assisted acquisition can recover useful Android artifacts and runtime state from non-root devices, supporting lightweight and repeatable collection workflows \cite{neth2023androidtriage}. Runtime network observation is also important for privacy assessment because third-party services and tracking relationships may become visible only after an application is launched or exercised. Paci et al.\ showed that execution-time observation is necessary to characterize third-party tracking behavior that cannot be inferred fully from packaged artifacts alone \cite{paci2023tracking}.

Runtime evidence must be interpreted within the conditions under which it was collected. A packet capture records activity from a particular application build, device, network environment, duration, and interaction sequence. It does not by itself establish malicious behavior or reveal the semantics of encrypted content. Contemporary time-series research similarly treats deviation as a measured departure from an observed baseline rather than direct proof of harmful intent \cite{mejri2024timeseries}. For Android studies, this distinction supports reporting traffic volume, packet timing, service relationships, and interaction-driven changes as behavioral evidence without equating statistical variation with compromise or privacy abuse.

Reproducibility is further complicated by current Android distribution practices. Google Play commonly generates device-specific APK sets from Android App Bundles, including a base APK and configuration or feature splits selected for the target device \cite{androidAppBundles2026}. Consequently, an isolated base APK may not represent the complete installed application. Reproducible analysis should retain the package name, version code and name, APK hashes, split membership, acquisition time, device context, and analysis identifiers associated with each observation. Application updates create an additional provenance problem because static and dynamic evidence collected from different versions should not be treated as interchangeable without explicitly documenting their relationship.

Privacy disclosure systems add another layer of evidence but do not replace technical measurement. Google Play's Data safety section lets developers describe how an app collects, shares, and handles data across versions distributed on Google Play \cite{googlePlayDataSafety2026}. Recent studies show why such disclosures need technical context. Khedkar et al.\ found that Android apps can under-report or over-report privacy-related data collection when compared with technical analysis \cite{khedkar2026privacydata}. Rodriguez et al.\ showed that SDK configuration and runtime behavior can create mismatches between developer choices, privacy labels, and application behavior \cite{rodriguez2025privacysettings}. This study therefore treats privacy disclosures and platform guidance as context, while the measured evidence comes from build-backed static and runtime artifacts.

The OWASP Mobile Application Security Verification Standard provides a structured vocabulary for organizing mobile security findings across storage, cryptography, authentication, network communication, platform interaction, resilience, and privacy \cite{owaspMasvs2024}. The associated Mobile Application Security Testing Guide provides techniques for evaluating these control areas \cite{owaspMastg2024}. In this study, MASVS categories are used to structure and compare evidence rather than to claim formal certification. Individual permissions, domains, exported components, and detector findings are therefore treated as contextual indicators, not as proof of exploitability.

This study applies these principles to 15 Android social media, messaging, and news applications. Static evidence characterizes declared capability and packaged exposure, while dynamic evidence records runtime network and behavioral observations under controlled conditions. The two evidence streams are linked through package, version, APK, run, packet-capture, and quality-assurance provenance. This design enables cross-application privacy and security analysis without assuming that evidence collected from different builds or execution conditions is directly interchangeable.
