\section{Methodology}

\subsection{Research Questions and Study Design}
The study is a descriptive, build-aligned analysis of 15 Android consumer apps. The unit of inference is the selected app build: package name, version code/name, base APK hash, split identity, contributing static run, and selected dynamic runs. RQ1 is addressed through static exposure variables; RQ2 through runtime evidence classes and network metadata; RQ3 through app-level integrated profiles and descriptive associations.

\subsection{Dataset, Device, and Collection Window}
Collection used a non-root Motorola moto g 5G 2024 running Android 15. The fixed recent-evidence window spans June 26 to July 9, 2026 UTC. A run or static result was eligible only when it could be tied to the selected package/version group and passed identity, validity, signal, and QA checks. Applications were grouped by primary user-facing function into News, Social Media, Messaging, and Professional Networking categories. The categories are used for descriptive visualization only and are not treated as statistical strata. The non-root setting avoids privileged instrumentation, app modification, TLS interception, and payload inspection.

\subsection{Static Analysis and Exposure Variables}
Static analysis used harvested base and split APK artifacts for the selected build. Variables include dangerous permission count, high/medium finding count, unguarded exported components, network-security findings, storage findings, privacy findings, platform findings, MASVS-aligned category counts, and SDK/service indicators where supported. These values are exposure indicators; they are not a calibrated exploitability score.

\subsection{Runtime Collection and Evidence Classes}
Runtime collection used package-associated dynamic evidence packs and PCAP metadata. Runs were classified as strict-idle, QFG, or interactive. Strict-idle captures represent foreground quiet-state baselines. QFG captures are no-touch foreground observations in which app-driven activity continued. Interactive captures exercise user-facing behavior. Runtime variables include run counts, duration, PCAP bytes, packet rate, domain count, service-family count, protocol prevalence, and baseline-relative shifts where both baseline and interactive evidence exist.

\subsection{Build Selection and Static-Runtime Alignment}
For each app, we selected a build group using package/version identity, base APK hash, static-run availability, dynamic-run availability, PCAP state, QA validity, and recency. Algorithm~\ref{alg:build-aligned-selection} summarizes the deterministic selection and reporting procedure. Static and runtime rows were included only when the selected static and dynamic evidence aligned to the same selected build group. Runs with mismatched build identity, missing static evidence, missing dynamic evidence, invalid QA state, or insufficient signal were excluded or deferred.

\begin{algorithm}[!t]
\caption{Build-Aligned Static-Runtime Evidence Selection}
\label{alg:build-aligned-selection}
\begin{algorithmic}[1]
\REQUIRE cohort $A$, 14-day window $W$, static set $S$, dynamic set $D$, qualification policy $P$
\ENSURE aligned app-build rows, excluded/deferred rows, source data, checksums
\FOR{each application $a \in A$}
  \STATE retrieve candidate dynamic runs for $a$ within $W$
  \STATE apply identity, evidence-validity, signal, PCAP, and QA requirements from $P$
  \STATE group qualifying runs by normalized package, version code, base APK SHA-256, and artifact/build-set identity
  \STATE identify build groups satisfying runtime evidence requirements
  \STATE select one group using the canonical deterministic build-ranking policy
  \STATE resolve static evidence in $S$ for the same selected build
  \IF{static and dynamic identities do not align}
    \STATE exclude or defer $a$; persist the reason; continue
  \ENDIF
  \STATE preserve strict-idle, QFG, and interactive classes separately
  \STATE compute static exposure and runtime behavior summaries
  \STATE add the aligned app-build row and provenance
\ENDFOR
\STATE compute descriptive cross-layer profiles and app-level associations
\STATE export aligned rows, excluded/deferred rows, source data, and checksums
\end{algorithmic}
\end{algorithm}

\subsection{Integrated Measures and Statistical Analysis}
Integrated analysis compares app-level static exposure with app-level runtime metadata. The paper reports descriptive counts, medians by evidence class, baseline-relative packet-rate shifts, and Spearman-style app-level associations only as exploratory summaries. For cross-layer grouping, apps are assigned by median split: higher static exposure uses high/medium finding volume greater than or equal to the cohort median, and higher runtime activity uses interactive domain count greater than or equal to the cohort median. Equality is assigned to the higher group. No opaque composite risk score is introduced.

\subsection{Privacy and Reproducibility Boundaries}
PCAP processing is limited to metadata and derived transport indicators. The study does not inspect message bodies, cookies, authorization headers, private account content, or decrypted TLS payloads. Reproducibility artifacts include source CSVs, generated \LaTeX{} tables, figure source data, and SHA-256 checksums for generated assets.

\subsection{Limitations and Threats to Validity}
The study is bounded by a 15-app dataset, one Android 15 physical device, selected user scenarios, available static detectors, and a non-root no-MITM PCAP privacy model. It does not claim exhaustive code coverage, decrypted payload semantics, or full Data Safety validation. Some apps have stronger interactive depth than others, and runtime findings are scenario-bounded. Static detector counts remain descriptive exposure indicators rather than formal exploitability or compliance scores. The integrated analysis is therefore intended to characterize cross-layer posture for selected builds, not to infer causation or predict future app behavior.
