\section{Discussion}

\subsection{Evidence Stability Under App-Update Churn}

The 14-day evidence window separates research readiness from the continuously changing operational queue. When a selected app build is captured within the window and linked to valid static and runtime evidence, a subsequent app-store update does not invalidate those observations. Instead, the newer build becomes a candidate for a future comparison wave. This approach prevents recent, version-backed measurements from being discarded solely because the installed application changed after collection, while preserving the package, version, APK, static-run, dynamic-run, and quality-assurance provenance needed to interpret each result.

This decision is especially important for popular consumer apps because update cadence can be faster than a complete static/runtime measurement cycle. Without a bounded recent-evidence rule, the study would either chase moving targets indefinitely or discard valid runs whenever an app updated after capture. The window therefore functions as an audit boundary: it preserves recency while keeping each claim tied to a concrete package version, APK hash, static run, dynamic run, and PCAP-derived feature set.

\subsection{Interpreting Static and Runtime Evidence}

Static and runtime evidence describe related but different aspects of Android app posture. Static analysis characterizes declared capabilities, packaged attack surface, exported components, permissions, configuration choices, and detector findings. Runtime analysis characterizes the network activity observed during selected idle, quiescent foreground, and interactive execution scenarios. A high static finding count does not necessarily imply broad runtime activity, while limited observed runtime activity does not demonstrate low privacy or security exposure. The integrated results should therefore be interpreted as cross-layer characterization rather than evidence of causation, prediction, exploitability, or malicious behavior.

This distinction is central to the results because the integrated matrix contains examples in every quadrant. Static-heavy apps warrant review of exported components, permission guards, SDKs, and packaged configuration even if the observed scenario is quiet. Runtime-heavy apps warrant scenario and service-family review even when static finding volume is lower. Concordant higher apps are the strongest candidates for deeper manual analysis because both layers point to elevated exposure.

\subsection{App-Level Profiles and Review Prioritization}

The app-level profiles illustrate why both evidence layers are needed. Static-heavy apps such as Snapchat and WhatsApp expose substantial packaged surfaces even when the selected runtime scenarios do not produce the broadest domain diversity. Lower-static but higher-runtime cases such as CNN and BBC News demonstrate that interactive network activity can broaden even when static finding volume is lower than that of large social platforms. Apps such as Facebook, Instagram, TikTok, and X exhibit higher values across both layers and may therefore warrant deeper manual examination. These profiles are intended to support review prioritization, not to function as composite risk scores or formal security rankings.

This framing is useful for security teams because it turns disagreement between static and runtime evidence into a triage signal rather than a reporting problem. A mismatch can suggest where the next review should go: static-heavy cases toward manifest and component review, runtime-heavy cases toward scenario design and network/service labeling, and concordant higher cases toward deeper manual assessment. The goal is not to collapse the layers into one score, but to preserve enough structure for defensible follow-up.

\subsection{QFG Separation and Practical Implications}

Separating quiescent foreground (QFG) captures from strict idle captures is an important methodological distinction. Social, news, and messaging apps may continue loading content, synchronizing services, or maintaining communication state while foregrounded but untouched. Counting this activity as strict idle would overstate baseline quietness, whereas discarding it would remove meaningful app-driven behavior. Reporting QFG as a separate evidence class preserves both interpretations. More broadly, the findings indicate that Android app assessment should not be reduced to either static inspection or runtime traffic observation alone. Build-aligned static and runtime evidence allows practitioners to compare declared exposure with observed behavior without combining measurements from different application versions.

The QFG class also improves comparability across app types. A content-feed app may refresh recommendations or media while untouched, whereas an encrypted messaging app may remain relatively quiet until a message, call, or synchronization event occurs. Treating both as ordinary idle would collapse different behaviors into one baseline. Keeping QFG separate allows the paper to describe app-driven foreground behavior without claiming that it represents user inactivity in the strictest sense.
