\section{Conclusion}

This paper presented a build-aligned static-runtime evidence model for assessing privacy and security posture in Android consumer applications. The central methodological problem is that popular apps update quickly enough that an all-current-build measurement wave can become unstable before collection finishes. The proposed 14-day evidence window addresses that problem by selecting recent, fully identified app-build groups and preserving package version, APK hash, static-run, dynamic-run, PCAP, collection-window, and QA provenance. At cutoff, all 15 applications had usable build-backed evidence and no true evidence holes, so the reported results refer to selected app builds rather than mutable installed-app state.

The results show why static and runtime evidence should be interpreted as complementary measurement layers. Static analysis exposed substantial variation in declared and packaged attack surface, including 1,235 high/medium findings and 955 unguarded exported components across the selected builds. Runtime analysis added evidence about observed behavior across 123 captures, including 44 strict-idle, 23 QFG, and 56 interactive runs. The median baseline-relative packet-rate shift was 3.39 on the log$_2$ scale, while the descriptive association between static finding volume and interactive domain count was near zero. These results do not imply exploitability, maliciousness, or prediction; instead, they show that static exposure and observed runtime behavior can diverge and should be reported with explicit provenance and evidence-class labels.

Future work should extend this cutoff model into longitudinal build-to-build comparisons, additional Android devices and OS versions, stronger held-out runtime validation, and improved service-family labeling for encrypted traffic metadata. The next step is not to replace build-backed provenance with a single composite score, but to use the same evidence contract across repeated collection windows so that app updates become measurable longitudinal events. In that form, ScytaleDroid can support repeatable Android app studies that preserve privacy boundaries while giving researchers and practitioners a clearer view of how declared capabilities, packaged exposure, and runtime behavior evolve over time.
