\section{Introduction}

Android consumer applications are now routine entry points for communication, media consumption, news, social networking, and personalized content delivery. These applications are not necessarily malicious, but they handle sensitive user data and interact with device capabilities, third-party software development kits (SDKs), cloud services, advertising systems, and cross-application interfaces. Android's permission model explicitly protects restricted data and restricted actions, while Google Play's Data safety section asks developers to describe collection, sharing, and security practices to users \cite{androidPermissions2026,googlePlayDataSafety2026}. The practical security question is therefore not only whether an application declares a sensitive capability, but whether the evidence surrounding a specific app build supports defensible privacy and security claims.

Prior Android security and privacy studies show why this question requires more than one evidence source. Static analysis can identify manifest exposure, requested permissions, exported components, storage settings, packaged resources, and SDK configuration, but static indicators do not establish how an application behaves during execution. Dynamic analysis can observe runtime network behavior, traffic shape, and interaction-dependent activity, but those observations are scenario-bounded and can be affected by device state, network conditions, app version, and user stimulation \cite{yang2022maniscope,wang2023runtimepermissions,sutter2024dynamic}. Recent privacy work further shows that developer disclosures, SDK behavior, and observed app practices may diverge \cite{rodriguez2025privacysettings,khedkar2026privacydata}. A sound study must therefore connect static exposure, runtime behavior, and provenance rather than reporting isolated detector outputs.

This paper presents Paper 3 in the ScytaleDroid Android research line: a 15-app empirical study of mainstream consumer applications using linked static and runtime evidence. The cohort spans social media, messaging, and news applications, including apps whose behavior is relevant to privacy, communications, platform interaction, and network security. The study is performed with ScytaleDroid, a database-backed Android analysis platform that links harvested base and split APKs, APK hashes, package and version identity, static findings, dynamic evidence packs, packet-capture availability, and quality-assurance status. The aim is methodological as well as empirical: to show how Android app risk can be reported in a way that is auditable, version-aware, and robust to app-update churn.

The central methodological challenge is that popular consumer apps update faster than a full all-current-build measurement wave can reliably complete. Treating the live installed build as the only paper gate would discard valid evidence whenever an app updates after collection. Paper 3 instead uses a fixed cutoff evidence model. At the final cutoff, all 15 apps had paper-usable, build-backed evidence bundles, and no true evidence holes remained. This does not mean that all 15 apps were current-build complete or that all runtime quotas were filled. It means that each app had usable evidence tied to a known package, version, APK set, static run, dynamic run, PCAP state, and QA outcome.

This paper makes the following contributions:
\begin{itemize}
    \item We present a 15-app Android consumer-app study that combines static APK evidence with runtime evidence from non-root physical-device collection.
    \item We introduce a cutoff-based evidence model that separates live operational current-build status from paper-ready build/version-backed evidence.
    \item We preserve package, version, APK hash, split membership, static run, dynamic run, PCAP, and QA provenance for app-level privacy and security claims.
    \item We distinguish strict idle, quiescent foreground, and interactive dynamic captures so that app-driven foreground activity is not misreported as strict idle behavior.
\end{itemize}

The remainder of this paper is organized as follows. Section~II provides background on Android app security evidence. Section~III positions the study relative to prior work. Section~IV describes the cohort, evidence model, static pipeline, and dynamic pipeline. Section~V presents the results. Section~VI discusses app-update churn, provenance-aware evidence collection, limitations, and future work. Section~VII concludes.
