\section{Methodology}

% IEEE CARS 2026 target baseline: 6-page conference paper.
% Target for this section: ~1.0--1.2 pages.
% Include enough detail for reproducibility and future extension.

\subsection{Artifact and Dataset Protocol}
TODO: Document the source, inclusion criteria, and labeling policy.
\begin{itemize}
  \item Artifact identifiers and provenance
  \item Inclusion/exclusion rules
  \item Baseline vs AI-assisted condition assignment
  \item Environment constraints and safety boundaries
\end{itemize}

\subsection{Static Analysis}
TODO: Define static indicators and tooling.
Track static indicators that are likely to be meaningful for defensive workflows, such as metadata fields,
string features, API-call profiles, imported modules, and entropy distributions.

\subsection{Dynamic and Behavioral Analysis}
TODO: Define controlled execution procedure and telemetry capture.
Collect runtime signals in isolation, including process-level activity, file/object modifications,
network attempts, and alert output from detection systems.

\subsection{Comparative Evaluation}
TODO: Specify comparison metrics and reporting.
Compare both conditions on paired metrics (baseline vs AI-assisted), using the same template for each item and the same analyst review rubric.

\subsection{Limitations}

A key challenge in this study was the churn of update of the app. During collection, several apps updated before the entire group could be completed on the same live installed-build state. Apps that had valid baseline or interactive evidence could later appear incomplete in the operational queue after a new version was installed. Treating the live current-build queue as the paper-readiness gate would therefore create a moving target. To avoid this problem, the study closes collection at a fixed cutoff and assembles app-level evidence bundles tied to package name, version code/name, APK hashes, static run identifiers, dynamic run identifiers, PCAP availability, and QA provenance.