\section{Results}

The final cutoff evidence bundle supports the core rough-draft claim: 15/15 Research Dataset Beta apps had paper-usable, build-backed evidence bundles at cutoff. The cutoff contained zero true evidence holes. This result should be interpreted as paper readiness under the cutoff evidence model, not as completion of every live current-build queue target and not as completion of the full operational quota target.

\begin{table}[htbp]
\caption{Paper 3 cutoff evidence tier summary.}
\label{tab:evidence-tier-summary}
\centering
\begin{tabular}{lr}
\toprule
Metric & Count \\
\midrule
Paper-usable apps & 15/15 \\
Strict current-build complete & 5 \\
Current-build mixed baseline & 2 \\
Prior-build paper evidence & 8 \\
True evidence holes & 0 \\
\bottomrule
\end{tabular}
\end{table}

The evidence tier split is the primary result. Five apps were classified as strict current-build complete: BBC News, CNN, LinkedIn, Telegram, and Signal. Two apps were classified as current-build mixed baseline: Pinterest and Snapchat. Eight apps were classified as prior-build paper evidence: Facebook, Facebook Messenger, The Guardian, Instagram, Reddit, X, WhatsApp, and TikTok. No app was classified as a true evidence hole.

\begin{table*}[t]
\caption{Research Dataset Beta evidence bundles at cutoff.}
\label{tab:cohort-evidence-bundles}
\centering
\scriptsize
\begin{tabular}{llrrrr}
\toprule
App & Tier & Strict idle & QFG & Baseline & Interactive \\
\midrule
BBC News & Strict current & 4 & 0 & 4 & 6 \\
CNN & Strict current & 4 & 1 & 5 & 7 \\
LinkedIn & Strict current & 3 & 1 & 4 & 4 \\
Telegram & Strict current & 3 & 0 & 3 & 4 \\
Signal & Strict current & 3 & 0 & 3 & 4 \\
Pinterest & Current mixed & 5 & 0 & 5 & 2 \\
Snapchat & Current mixed & 1 & 2 & 3 & 2 \\
Facebook & Prior build & 3 & 1 & 4 & 4 \\
Facebook Messenger & Prior build & 4 & 0 & 4 & 5 \\
The Guardian & Prior build & 3 & 2 & 5 & 4 \\
Instagram & Prior build & 2 & 4 & 6 & 1 \\
Reddit & Prior build & 2 & 3 & 5 & 1 \\
X & Prior build & 3 & 1 & 4 & 4 \\
WhatsApp & Prior build & 4 & 0 & 4 & 5 \\
TikTok & Prior build & 0 & 8 & 8 & 3 \\
\bottomrule
\end{tabular}
\end{table*}

The current-build mixed-baseline category requires careful wording. Pinterest and Snapchat are paper-usable on the selected current build, but their evidence must separate strict idle, QFG/no-touch foreground, and interactive classes. For Snapchat, the selected current build includes one strict idle baseline, two QFG captures, and two interactive captures. These are usable for the paper only when QFG is reported as app-driven foreground activity rather than strict idle.

The prior-build category is also paper-usable, but it carries a provenance caveat. For the eight prior-build apps, the selected evidence is valid, static-linked, and PCAP-backed, but it must remain labeled as retained prior-build evidence. These rows support claims about the selected build-backed evidence bundle; they do not support a claim that the live installed build at cutoff was fully current-build complete.

The dynamic evidence-class table shows why class separation matters. Some apps have strong strict-idle and interactive coverage, while others have meaningful QFG or retained prior-build evidence that is useful but must be labeled. TikTok, for example, has QFG-heavy prior-build evidence and should not be described as strict-idle complete. Snapchat has current-build mixed evidence and should not be over-summarized as strictly idle-complete.
